Turbulence in compact to giant H~II regions

### 2022-11-29 strucfunc_paper.tex
Javier changes 2022-11-28

In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structure functions of some \hii{} regions of our sample.
In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
Finally, in the section \ref{power-law-index} we discuss the role of the derived power-law index in the context of turbulence in the ionized gas.

@@

% The diversity of methodologies used in prior studies 
% In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
% Since this is the first time a model of this type is applied to a sample of HII regions, our results are bounded to be different from previous investigations, including the investigations that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.

@@

\subsubsection{The constancy of the power law slope}
\label{sec:constancy-power-law}
The slope \(m\) of the power-law portion of the structure function
shows no significant correlation with any other parameter
(see Table~\ref{tab:RestStats}),
with a weighted mean value of \(m = 1.01\).
The dispersion in fitted \(m\) values is 1.6 times higher than expected
on the basis of the confidence limits for the individual regions,
implying that there may be a real intrinsic dispersion of 0.17 in the slopes.
However, a \(\chi^2\) test shows that this is only marginally significant
(\(p = 0.11\), so we cannot reject the idea that all the slopes are identical.

@@

% The second-order structure function measures the velocity fluctuations in the \hii{} regions under the assumption that there exists an underlying velocity spectrum following an energy cascade.
% But this statistical technique is not unique in measuring the velocity fluctuations in the nebula.
% Two parameters which can be obtained from the velocity profile also measure the velocity fluctuations in the \hii{} regions: the standard deviation of the velocity centroids, \(\sigma\pos\), and the mean non-thermal linewidth, \(\langle \sigma_{\text{los}} \rangle\).
% These quantities allow us to compare the relationship between the kinematical disorder on the plane-of-the-sky and along the line-of-sight \citep{2011MNRAS.413..705L,arthur2016turbulence}.

% The \( \sigma_{\text{los}} \) parameter is estimated by correcting the observed linewidth for the contribution of broadening mechanism, equation \eqref{eq:sigma-los}, leaving just the random motions which are interpreted as random motions along the line-of-sight.
% This method is a simplification of the problem since it assume a Gaussian profile fit, which does not consider other components that could arise from different kinematics processes of the ionized gas and leaves out the broadening due to dust scattering \citep{castaneda1988,1998ApJ...503..760H}.

@@

%the model fit to

@@

The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
With other 3 B-type stars they form the Trapezium cluster.
The bright region that surrounds these massive ionizing stars is called the Huygens region.
%In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.

@@

Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
In this case we merge the first three points of the structure function.
A detailed description of the model fit is given in
section~\ref{sec:example-results-orion} and will
not be repeated here.
At the largest scales, which are not used in the model fitting,
one sees a downturn in the structure function from
\SI{22}{km^{2}.s^{-2}} for \(r < \SI{0.3}{pc}\) to
\SI{7}{km^{2}.s^{-2}} at \(r  \SI{0.5}{pc}\)
(open symbols in Figure~\ref{fig:strucfunc-fit-Galactic}a).
This is similar to the behavior expected for tapered fluctuations
(see section~\ref{sec:limit-model-struct} and Figure~\ref{fig:model-strucfunc}b)
in which the velocity dispersion is higher in the center of the map
than in the periphery.

@@

The seeing width is much smaller than the angular scale of the observations
\subsubsection{Comparison with previous studies}
\label{sec:comparison-orion}

@@

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

@@

The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
%There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first two points.
The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
%The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

@@

The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
The most luminous star is the blue variable $\eta$ Car.
As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}. 
This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.

@@

(The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
%The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
For this region we merge the first two points of the structure function.
As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
%The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).

@@

The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
In this case we merge the first five points of the structure function.
%The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one %point of the structure function is below this value.
%Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.

@@

NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.30}{pc} ; \citealp{2001ApJ...562..303D}}. 
It has more than 30 O stars that ionize N66, the largest \hii{} region \citep{2011ApJ...740...10D}.
N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
\citet{2008ApJ...688.1050G} propose an expanding \hii{} region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionization from the OB stars. 
This mechanism is similar to shell-like \hii{} regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}.

@@

The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
%In this case we merge the first three points of the structure function.
%The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
For this region the first ten points lie below the true model.
At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
%The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.

@@

\subsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%
The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest \hii{} regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}} for HX and \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.
Two recognized OB associations are identified within these \hii{} regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.

@@

In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
%The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
%All the structure function points lies below the true model.
%The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.

@@

M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
The two brightest \hii{} regions in the galaxy are NGC 604 and NGC 595.

NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{17.8 \pm 0.3}{km.s^{-1}} \citep{1986A&A...160..374H}.
Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
For the northern cluster they find eight luminous stars and no evolved massive stars.
More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
This suggest that two episodes of star formation, at least, have taken place in the GEHR.

@@

NGC 595 is the second brightest giant \hii{} region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{16.8 \pm 0.1}{km.s^{-1}} \citep{lagrois2009multi}.
\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.

>>>>

%In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structure functions of some \hii{} regions of our sample.
%In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
%Finally, in the section \ref{power-law-index} we discuss the role of the derived power-law index in the context of turbulence in the ionized gas.

@@

@@

\subsubsection{The constancy of the power law slope}
\label{sec:constancy-power-law}
The slope \(m\) of the power-law portion of the structure function
shows no significant correlation with any other parameter
(see Table~\ref{tab:RestStats}),
with a weighted mean value of \(m = 1.01\).
The dispersion in fitted \(m\) values is 1.6 times higher than expected
on the basis of the confidence limits for the individual regions,
implying that there may be a real intrinsic dispersion of 0.17 in the slopes.
However, a \(\chi^2\) test shows that this is only marginally significant
(\(p = 0.11\)), so we cannot reject the idea that all the slopes are identical.

@@

@@

@@

The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} or \SI{e37.18}{erg.s^{-1}}. 
With other 3 B-type stars they form the Trapezium cluster.
The bright region that surrounds these massive ionizing stars is called the Huygens region.
%In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.

@@

%Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
%In this case we merge the first three points of the structure function.
%A detailed description of the model fit is given in
%section~\ref{sec:example-results-orion} and will
%not be repeated here.
At the largest scales, which are not used in the model fitting,
one sees a downturn in the structure function from
\SI{22}{km^{2}.s^{-2}} for \(r < \SI{0.3}{pc}\) to
\SI{7}{km^{2}.s^{-2}} at \(r  \SI{0.5}{pc}\).
%This is similar to the behavior expected for tapered fluctuations
%(see section~\ref{sec:limit-model-struct} and Figure~\ref{fig:model-strucfunc}b)
%in which the velocity dispersion is higher in the center of the map
%than in the periphery.

@@

%The seeing width is much smaller than the angular scale of the observations
\subsubsection{Comparison with previous studies}
\label{sec:comparison-orion}

@@

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
%It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
%The velocity field shows several expanding shells, related to the stellar population, and the massive %protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
%A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
%The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

@@

The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
%There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
%In this case we merge the first two points.
%The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
%The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

@@

The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
%Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
%This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
The most luminous star is the blue variable $\eta$ Car.
%As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}. 
%This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.

@@

(The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
%For this region we merge the first two points of the structure function.
%As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
%The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).

@@

The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
%NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
%In this case we merge the first five points of the structure function.
%The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one %point of the structure function is below this value.
%Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.

@@

NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.30}{pc} ; \citealp{2001ApJ...562..303D}}. 
It has more than 30 O stars that ionize N66, the largest \hii{} region \citep{2011ApJ...740...10D}.
N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
%\citet{2008ApJ...688.1050G} propose an expanding \hii{} region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionization from the OB stars. 
%This mechanism is similar to shell-like \hii{} regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}.

@@

The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
%In this case we merge the first three points of the structure function.
%The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
%For this region the first ten points lie below the true model.
At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
%The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.

@@

\subsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%
The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest \hii{} regions are Hubble X and Hubble V.
Luminosity IN \ha{} for Hubble V is \SI{e38.3}{erg.s^{-1}} and for Hubble X is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}} for HX and \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.
Two recognized OB associations are identified within these \hii{} regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
%HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
%\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.

@@

In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
%For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
%The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
%All the structure function points lies below the true model.
%The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.

@@

M33 is the third largest galaxy in the Local Group located at the distance of 820 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
The two brightest \hii{} regions in the galaxy are NGC 604 and NGC 595.

NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{17.8 \pm 0.3}{km.s^{-1}} \citep{1986A&A...160..374H}.
Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
%In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
%For the northern cluster they find eight luminous stars and no evolved massive stars.
%More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
%\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
%The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
%This suggest that two episodes of star formation, at least, have taken place in the GEHR.

@@

NGC 595 is the second brightest giant \hii{} region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{16.8 \pm 0.1}{km.s^{-1}} \citep{lagrois2009multi}.
\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
%They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
%\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
%They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
%\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
%They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
